\Large \bf \Toolname: Precise False Sharing Detection for COTS Binaries

### 2014-11-05 HotOS'15/paper.tex
Still need to do the subsection on proxy memory.

\paragraph{Contributions}
This paper makes the following significant contributions:
\begin{itemize}
\item It presents \Toolname{}, a software-only framework that dynamically and precisely diagnoses
false sharing  in multi-threaded, CTOS binaries. We believe that operating directly on binaries is
important because it allows one to verify observed performance problems using the same binaries
that are running in a production environment.

@@

\subsection{Race Detection}

@@

\subsection{False Sharing Detection}

@@

The remainder of this section explains how we vary the detection granularity (\Secref{proxymem}), how we use sampling
to detect contending accesses to shared memory (\Secref{heapsample}), how we reduce false negatives with our
sampling-based approach (\Secref{falsenegs}), and finally how we rank discovered instances of false sharing (\Secref{ranking})

\subsection{Proxy Memory and Tagged Reads}\label{sec:proxymem}

\subsection{Heap Sampling}\label{sec:heapsample}

\subsection{Reducing False Negatives}\label{sec:falsenegs}

@@

We perform two separate analyses to extend belief sets: \begin{description}
\item[Type Analysis] \hfill \\
This analysis instruments all code and identifies what types of objects are accessed by what code. Object types are loosely
defined as \TypeIdPair{} pairs, where $PC$ is the return address of an allocation function, and $size$ is the number of bytes
being allocated. To each \TypeIdPair pair, we associate a unique \TypeId{}. We taint \cite{AddressWatchpoints} allocated
addresses with their \TypeId{}, and propagate this taint to code accessing typed data.

@@

\subsection{Ranking}\label{sec:ranking}

>>>>

\paragraph{Contributions}
This paper makes the following significant contributions:
\begin{itemize}
\item It presents \Toolname{}, a software-only framework that dynamically and precisely diagnoses
false sharing  in multi-threaded, COTS binaries. We believe that operating directly on binaries is
important because it allows one to verify observed performance problems using the same binaries
that are running in a production environment.

@@

% --------------------------------------
\subsection{Race Detection}

@@

% --------------------------------------
\subsection{False Sharing Detection}

@@

The remainder of this section explains how we proxy memory access behavior (\Secref{proxymem}), how we use sampling
to detect contending accesses to shared memory (\Secref{heapsample}), how we reduce false negatives with our
sampling-based approach (\Secref{falsenegs}), how we achieve precision by eliminating false positives (\Secref{falsepos}),
and finally how we rank discovered instances of false sharing (\Secref{ranking})

% --------------------------------------
\subsection{Proxy Memory and Tagged Reads}\label{sec:proxymem}

Proxy memory is a form of read-only shadow memory that summarizes or proxies actual memory access behavior. The key
idea  .... TODO!!

% --------------------------------------
\subsection{Heap Sampling}\label{sec:heapsample}

\Toolname{} follows DataCollider's sampling based approach, but samples proxy memory instead of code \cite{DataCollider}.
\Toolname{} applies the roughly the following high-level algorithm to sample proxy memory and detect potential false sharing:
\begin{enumerate}
\item Choose a proxy memory address $P$ uniformly at random. Add a hardware watchpoint $w(P)$ to $P$.
\item If the watchpoint $w(P)$ is not triggered within $t$ units of time, then remove $w(P)$ and go to step (1).
\item If $w(P)$ is triggered for thread $T_i$ then pause $T_i$ for $t$ units of time. The hope is that within this
time slice, another thread, $T_j$ will be caught in the act of false sharing by triggering $w(P)$.
\item If $w(P)$ is not triggered again for another $t$ time units, then remove $w(P)$ and go to step (1).
\item If another thread $T_j$ triggers $w(P)$, then record stack traces for $T_i$ and $T_j$, and mark the associated program
counters of each of $T_i$ and $T_j$ as potentially having false sharing.
\item Go to step (1) to repeat the process for a new sample location.
\end{enumerate}

As described, our sampling algorithm is susceptible to bias: if only a small percentage of the application's data is concurrently
modified, or ``hot", then our algorithm might miss potential false sharing by wasting time sampling from the cold data.
To avoid this issue, we apply two new techniques: \emph{uniform heap sampling}, and \emph{selective heap sampling}.

\paragraph{Uniform Heap Sampling}
Uniform heap sampling is a round-robin algorithm that uniformly selects proxy memory locations to sample according to
the types of data proxied. We interpose on memory allocation and deallocation routines (e.g. \texttt{malloc} and \texttt{free})
and associate unique \TypeId{}s to each \TypeIdPair{}, where $PC$ is the return address of an allocation function, and $size$ is the
number of bytes allocated.

For each proxy memory location $P$, we maintain a counting \emph{typeset}: a mapping of \TypeId{}s to the number of objects of type
\TypeId{} that are fully or partially proxied by $P$.

\paragraph{Selective Heap Sampling}
Selective heap sampling is a biased variant of uniform heap sampling that allows a user to guide the sampler to only focus
on specific types of data. This is beneficial when one is trying to solve specific performance problems related to a subset
of the data being accessed by the application.

% --------------------------------------
\subsection{Reducing False Negatives}\label{sec:falsenegs}

@@

We perform two separate analyses to extend belief sets: \begin{description}
\item[Type Analysis] \hfill \\
This analysis instruments all code and identifies what types of objects are accessed by what code. We apply the same
notion of typesets as used in the uniform heap sampler; however, in this case typesets are associated with basic
blocks of code instead of with proxy memory. We use address watchpoints \cite{AddressWatchpoints} to taint
allocated addresses with their \TypeId{}, and then propagate these \TypeId{}s to the typesets of the blocks operating
of data of each type.

@@

% --------------------------------------
\subsection{Eliminating False Positives}\label{sec:falsepos}

We apply two techniques to reduce and finally eliminate false positives:
\begin{enumerate}
\item We iteratively refine the granularity of proxy memory, starting from the page granularity and going down to the cache
line granularity. As the granularity is refined and potential false sharing continues to be detected, our confidence in beliefs
of false sharing improves.

\item We apply a precise data race detector \cite{DataCollider} to instructions that demonstrate cache line contention. This
allows us to distinguish between true and false sharing.
\end{enumerate}

Distinguishing between false sharing and pseudo sharing is more challenging. We approximate this detection by extending
the type analysis phase to record the relative byte offset within each type of accessed object for each instruction. If false
sharing is detected between two instructions operating on the same offset ($\pm$ the memory access size), then we report
pseudo sharing, otherwise false sharing. Another valid heuristic would include the natural alignment and sizes of object
types.

% TODO: How to make it precise? Apply DataCollider to places where we've found potential false sharing at the granularity
% of a cache line.

% How do we distinguish between false sharing and pseudo sharing? Use the type analysis feature to figure out what offsets
% into what data were being accessed.h

% --------------------------------------
\subsection{Ranking}\label{sec:ranking}
